Flaring star-planet interactions in star-planet systems in Kepler and TESS

### 2023-05-12 src/tex/ms.tex
[showyourwork] overleaf sync

@@

We applied the same technique as described in Section~\ref{sec:methods:adtest} to determine the significance of a local tidal SPI signal. Since we lack a model to relate tidally induced flaring to the systems' properties, we follow~\citet{ilic2022tidal}, and compare the resulting $p$-values with three different models of tidal interaction as proxies for expected excess flaring due to tides in Fig.~\ref{fig:tidal}. We list the derived values in Table~\ref{tab:tidal}.

@@

We collect the planetary and stellar masses from the literature~(Table~\ref{tab:tidal}). For missing planetary masses, the radii were known, so used the mass-radius relations implemented in \texttt{forecaster}~\citep{chen2017probabilistic}. GJ 3323, GJ 674 and GJ 3082 were also missing stellar mass estimates, which we obtained from the \citep{mann2015how, mann2016erratum} relations between absolute Ks magnitude~\citep{skrutskie2006two} and stellar mass for M dwarfs using the distances from \citet{bailer-jones2021estimating}. We list the masses in Table~\ref{tab:tidal}.

We find that no single system shows significant signs of tidal star-planet interaction. Overall, the signal in phase with $P_{orb}/2$ is smaller than with $P_{orb}$. However, in all three scenarios, the deviation from random flare timing increases with expected tidal interaction strength. We can now compare the magnetic interaction measurements to the tidal ones in some of the conspicuous systems:

>>>>

\subsubsection{Comparison to tidal interaction scaling laws}

@@

We applied the same technique as described in Section~\ref{sec:methods:adtest} to determine the significance of a local tidal SPI signal. Since we lack a model to relate tidally induced flaring to the systems' properties, we follow~\citet{ilic2022tidal}, and compare the resulting $p$-values with three different scaling laws for tidal interaction as proxies for expected excess flaring due to tides in Fig.~\ref{fig:tidal}. We list the derived values in Table~\ref{tab:tidal}.

@@

\subsubsection{Planetary and stellar masses}

We collect the planetary and stellar masses from the literature~(Table~\ref{tab:tidal}). For missing planetary masses, the radii were known, so used the mass-radius relations implemented in \texttt{forecaster}~\citep{chen2017probabilistic}. GJ 3323, GJ 674 and GJ 3082 were also missing stellar mass estimates, which we obtained from the \citep{mann2015how, mann2016erratum} relations between absolute Ks magnitude~\citep{skrutskie2006two} and stellar mass for M dwarfs using the distances from \citet{bailer-jones2021estimating}. We list the masses in Table~\ref{tab:tidal}. For Kepler-42 b, we used  $M_p=0.1-2.06M_\oplus$ that covers pure rock to pure iron compositions in \citet{muirhead2012characterizing}.

\subsection{Tidal vs. magnetic flaring star planet interaction}

We find that no single system shows significant signs of tidal star-planet interaction. Overall, the signal in phase with $P_{orb}/2$ is smaller than with $P_{orb}$. However, in all three scenarios, the sample's deviation from random flare timing increases with expected tidal interaction strength. We can compare the magnetic interaction measurements to the tidal ones in some of the conspicuous systems:
